Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-07-26 paper.Rnw
updated explanation scatterplot
more updates after limeaid updates to the explanation scatterplot

\subsection{LIME Assessment Visualizations}

@@

Figure \ref{fig:bullet-eois} include the explanation plots (from \emph{lime}) and explanation scatterplots for cases M and NM. Plots for 3 equal bins and 3 quantile bins are included. The scatterplots provide several insights into the LIME explanations. Here we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.

@@

\begin{figure*}[!thp]
<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 17, fig.align = "center", out.width="90%", message = FALSE>>=
# Join the plots
plot_grid(
  pf2_3qb,
  pf2_3eb,
  eoi2_3qb,
  eoi2_3eb,
  pf1_3qb,
  pf1_3eb,
  eoi1_3qb,
  eoi1_3eb,
  nrow = 4,
  rel_heights = c(0.2, 0.3, 0.2, 0.3)
)
@
\caption{Plots of LIME explanations and explanation scatterplots for one case M and NM in the bullet test data. The first column contains plots associated with 3 quantile bins and the second with 3 equally spaced bins. The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
\label{fig:bullet-eois}
\end{figure*}

@@

\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, heighest weights in ridge regression, LASSO, classification/regression tree splits

@@

>>>>

\subsection{LIME Assessment Visualizations} \label{bullet-assess-ex}

@@

Figure \ref{fig:bullet-eois} include the explanation plots (from \emph{lime}) and explanation scatterplots for cases M and NM. Plots for 3 equal bins and 3 quantile bins are included. Plots for the kernel density simulation method are included in Figure \ref{fig:bullet-expl-scat-density}. The scatterplots provide several insights into the LIME explanations. Here we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.

@@

\begin{figure*}[!thp]
<<bullet-eois, out.width = '\\textwidth', fig.width = 12, fig.height = 17, fig.align = "center", out.width="90%", message = FALSE>>=
# Join the plots
plot_grid(
  pf2_3qb,
  pf2_3eb,
  eoi2_3qb,
  eoi2_3eb,
  pf1_3qb,
  pf1_3eb,
  eoi1_3qb,
  eoi1_3eb,
  nrow = 4,
  rel_heights = c(0.2, 0.3, 0.2, 0.3)
)
@
\caption{Plots of LIME explanations and explanation scatterplots for one case M and NM in the bullet test data. The first column contains plots associated with 3 quantile bins and the second with 3 equally spaced bins. The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
\label{fig:bullet-eois}
\end{figure*}

@@

\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, highest weights in ridge regression, LASSO, classification/regression tree splits

@@

Figure \ref{fig:bullet-expl-scat-density} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.

\begin{figure*}[!thp]
<<bullet-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 9, fig.align = "center">>=
bullet_es_NM <-
  plot_explain_scatter(
  bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
  alpha = 0.75, title.opt = TRUE
) +
  theme_bw(base_family = "Times") +
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.placement = "outside")

bullet_es_M <-
  plot_explain_scatter(
  bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
  alpha = 0.75, title.opt = TRUE
) +
  theme_bw(base_family = "Times") +
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.placement = "outside")

plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
@
\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
\label{fig:bullet-expl-scat-density}
\end{figure*}
